`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-17 inst/manuscript/manuscript.rmd
Switch from stale bmc-bioinformatics to current biomed-central.csl citation style definition;

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon^‡^
  and Johannes Graumann ^†,§,^*
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  pdf_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
csl: bmc-bioinformatics.csl
bibliography: flippant.bib
---

>>>>

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon^‡^
  and Johannes Graumann ^†,§,^*
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  pdf_document:
    fig_caption: yes
  html_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
csl: biomed-central.csl
bibliography: flippant.bib
---
